
% This LaTeX was auto-generated from an M-file by MATLAB.
% To make changes, update the M-file and republish this document.



    
    

\subsection*{sq\_dist.m} 

\begin{par}
sq\_dist - a function to compute a matrix of all pairwise squared distances between two sets of vectors, stored in the columns of the two matrices, a (of size D by n) and b (of size D by m). If only a single argument is given or the second matrix is empty, the missing matrix is taken to be identical to the first.
\end{par} \vspace{1em}
\begin{par}
Special functionality: If an optional third matrix argument Q is given, it must be of size n by m, and in this case a vector of the traces of the product of Q' and the coordinatewise squared distances is returned.
\end{par} \vspace{1em}
\begin{par}
NOTE: The program code is written in the C language for efficiency and is contained in the file sq\_dist.c, and should be compiled using matlabs mex facility. However, this file also contains a (less efficient) matlab implementation, supplied only as a help to people unfamiliar with mex. If the C code has been properly compiled and is avaiable, it automatically takes precendence over the matlab code in this file.
\end{par} \vspace{1em}
\begin{par}
Usage: C = sq\_dist(a, b)    or: C = sq\_dist(a)  or equiv.: C = sq\_dist(a, [])    or: c = sq\_dist(a, b, Q) where the b matrix may be empty.
\end{par} \vspace{1em}
\begin{par}
where a is of size D by n, b is of size D by m (or empty), C and Q are of size n by m and c is of size D by 1.
\end{par} \vspace{1em}
\begin{par}
Copyright (c) 2003, 2004, 2005 and 2006 Carl Edward Rasmussen. 2006-03-09.
\end{par} \vspace{1em}

\begin{lstlisting}
function C = sq_dist(a, b, Q);
\end{lstlisting}


\subsection*{Code} 


\begin{lstlisting}
if nargin < 1 | nargin > 3 | nargout > 1
  error('Wrong number of arguments.');
end

if nargin == 1 | isempty(b)                   % input arguments are taken to be
  b = a;                                   % identical if b is missing or empty
end

[D, n] = size(a);
[d, m] = size(b);
if d ~= D
  error('Error: column lengths must agree.');
end

if nargin < 3
  C = zeros(n,m);
  for d = 1:D
    C = C + (repmat(b(d,:), n, 1) - repmat(a(d,:)', 1, m)).^2;
  end
  % C = repmat(sum(a.*a)',1,m)+repmat(sum(b.*b),n,1)-2*a'*b could be used to
  % replace the 3 lines above; it would be faster, but numerically less stable.
else
  if [n m] == size(Q)
    C = zeros(D,1);
    for d = 1:D
      C(d) = sum(sum((repmat(b(d,:), n, 1) - repmat(a(d,:)', 1, m)).^2.*Q));
    end
  else
    error('Third argument has wrong size.');
  end
end
\end{lstlisting}
